### 2019-03-01 results.tex
mz - spell check

Hyperparameter configuration for Multi-Regression is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} non-emtpy potential subsets (for $N$ input time series).
For this application, the default parameterization is the 
full set of input time series (8 in this case).
The test dataset is a time 
series of the outdoor temperature (ground truth) 
over the same period.  
The application makes 
predictions for each of these outdoor temperatures
using the regression coefficients constructed from the training set
for each new value in the test set.
%and computes and returns the MSE between predicted 
%and ground truth value pairs.

@@

Seneca deploys the applications automatically over AWS Lambda
and extracts execution time and memory use from 
AWS CloudWatch~\cite{ref:awscloudwatch} logs.
We compute monetary cost using the AWS Lambda pricing model~\cite{ref:pricing}.
Each function downloads the training/testing dataset 
of the application from AWS S3 upon function invocation. 
We do not consider the cost of dataset storage 
in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is under 2.5 cents for storage and request combined in a month.
%\footnote{\url{https://aws.amazon.com/cloudwatch/}}
%\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
We also evaluate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the applications using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Even though \texttt{maximum memory used} reported by AWS CloudWatch can fluctuate, we 
have verified that the optimized allocated memory is sufficient for all 
hyperparameter configurations to complete successfully.  We have also verified
that the memory requirements across hyperparemeter settings do not vary 
significantly. We plan to consider applications for which hyperparameter settings require
different maximum memory sizes as part of future work.

@@

Table~\ref{tab:cost_optimized} illustrates two important points.
First, using AWS Lambda, full hyperparameter space exploration is inexpensive in
\textit{absolute} dollar cost terms and Seneca's automatic memory size optimization
decreases this cost further.  Second, memory optimization reduces cost but can 
increase the total execution time for parameter search 
since the functions must operate under additional memory 
constraints (versus using the maximum allocated memory).  
In addition, this cost fluctuates depending on the quality of the Lambda
execution environment (number of CPUs, Linux container overhead, 
multitenency, etc.).  We omit this data due to space constraints but analyze it here.
The average absolute difference in cost
across the five applications (30 runs) is \$0.05. %I use only split 1 for all 5
%numbers are below
Moreover, we have verified that the highest cost of execution under 
optimized memory is still cheaper than the lowest cost of execution under maximum 
memory for all five applications.
%$	Ave Cost	Highest Cost	Lowest Cost	Diff (High - low)
%Prophet	0.215	0.294	0.178	0.116
%Multi_Reg	0.076	0.078	0.075	0.003
%SVC_1	0.015	0.015	0.015	0.001
%SVC_2	0.014	0.016	0.013	0.003
%XGBoost_1	0.586	0.632	0.510	0.122
%XGBoost_2	0.607	0.630	0.569	0.061
%NN_1	0.055	0.059	0.051	0.007
%NN_2	0.058	0.061	0.056	0.005

>>>>

Hyperparameter configuration for Multi-Regression is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} non-empty potential subsets (for $N$ input time series).
For this application, the default parameterization is the 
full set of input time series (8 in this case).
The test dataset is a time 
series of the outdoor temperature (ground truth) 
over the same period.  
The application makes 
predictions for each of these outdoor temperatures
using the regression coefficients constructed from the training set
for each new value in the test set.
%and computes and returns the MSE between predicted 
%and ground truth value pairs.

@@

Seneca deploys the applications automatically over AWS Lambda
and extracts execution time and memory use from 
AWS CloudWatch~\cite{ref:awscloudwatch} logs.
We compute monetary cost using the AWS Lambda pricing model~\cite{ref:pricing}.
Each function downloads the training/testing dataset 
of the application from AWS S3 upon function invocation. 
We do not consider the cost of dataset storage 
in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is less than 2.5 cents for storage and request combined in a month.
%\footnote{\url{https://aws.amazon.com/cloudwatch/}}
%\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
We also evaluate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the applications using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Even though \texttt{maximum memory used} reported by AWS CloudWatch can fluctuate, we 
have verified that the optimized allocated memory is sufficient for all 
hyperparameter configurations to complete successfully.  We have also verified
that the memory requirements across hyperparameter settings do not vary 
significantly. We plan to consider applications for which hyperparameter settings require
different maximum memory sizes as part of future work.

@@

Table~\ref{tab:cost_optimized} illustrates two important points.
First, using AWS Lambda, full hyperparameter space exploration is inexpensive in
\textit{absolute} dollar cost terms and Seneca's automatic memory size optimization
decreases this cost further.  Second, memory optimization reduces cost but can 
increase the total execution time for parameter search 
since the functions must operate under additional memory 
constraints (versus using the maximum allocated memory).  
In addition, this cost fluctuates depending on the quality of the Lambda
execution environment (number of CPUs, Linux container overhead, 
multitenancy, etc.).  We omit this data due to space constraints but analyze it here.
The average absolute difference in cost
across the five applications (30 runs) is \$0.05. %I use only split 1 for all 5
%numbers are below
Moreover, we have verified that the highest cost of execution under 
optimized memory is still cheaper than the lowest cost of execution under maximum 
memory for all five applications.
%$	Ave Cost	Highest Cost	Lowest Cost	Diff (High - low)
%Prophet	0.215	0.294	0.178	0.116
%Multi_Reg	0.076	0.078	0.075	0.003
%SVC_1	0.015	0.015	0.015	0.001
%SVC_2	0.014	0.016	0.013	0.003
%XGBoost_1	0.586	0.632	0.510	0.122
%XGBoost_2	0.607	0.630	0.569	0.061
%NN_1	0.055	0.059	0.051	0.007
%NN_2	0.058	0.061	0.056	0.005
